\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-04 coqimpl.tex
Fix typo.

We can also use "Family" and "SealFamily" to scope a (nested) family. The resulting family only support direct inheritance or "Override" (i.e. we can only override a sealed family as a whole together)---we will later explain this design decision and its usage, especially on resolving \ref{chg:definitional-relevant-reasoning}. What's more, "Override" family can only apply to sealed family as well (not allowed on normal family).

We can inherit a top-level family "parent" using \mintinline{Coq}{Family ... extends parent} as a new top-level family. As expected, "Override"
will override a field from the parent. "Inherit" can be used to inherit
nested families, inductive types, and fields. "Final" is used to claim that the decorated field is non-overridable, and later we will show how it is used to resolve\ref{chg:definitional-relevant-reasoning}. The fields inside a family
are order-sensitive because we have dependent types here. So "Inherit
Until" is used if the user wants to inherit a range of fields.  "Extend Family" is used only inside a inheriting family. Thus nested
family can only be inherited or extended together with its belonging family
(i.e. ultimately top level family), thus our support of family polymorphism is
incomplete.

>>>>

We can also use "Family" and "SealFamily" to scope a (nested) family. The resulting family only support direct inheritance or "Override" (i.e. we can only override a sealed family as a whole together)---we will later explain this design decision and its usage, especially on resolving \ref{chg:definition-relevant-reasoning}. What's more, "Override" family can only apply to sealed family as well (not allowed on normal family).

We can inherit a top-level family "parent" using \mintinline{Coq}{Family ... extends parent} as a new top-level family. As expected, "Override"
will override a field from the parent. "Inherit" can be used to inherit
nested families, inductive types, and fields. "Final" is used to claim that the decorated field is non-overridable, and later we will show how it is used to resolve \ref{chg:definition-relevant-reasoning}. The fields inside a family
are order-sensitive because we have dependent types here. So "Inherit
Until" is used if the user wants to inherit a range of fields.  "Extend Family" is used only inside a inheriting family. Thus nested
family can only be inherited or extended together with its belonging family
(i.e. ultimately top level family), thus our support of family polymorphism is
incomplete.
